State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small changes to paper and code

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
% \documentclass[12pt]{iopart}

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
 \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
 \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
\usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
% 
% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org} 
\begin{abstract}
	Will do the abstract towards the end. 
\end{abstract}

@@

\begin{figure}[!hb] 
% \renewcommand*{\thesubfigure}{}
\centering
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePSDPy.pdf}}
\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}

\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.

@@

\begin{align}\label{eq:IntegralOfGaussian}

@@

\end{align}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
\documentclass[12pt]{iopart}

%<-comment out this for checking equations (author list too)
\usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
 % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
 \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
% \usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}

\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org} 
\begin{abstract}
	Will do the abstract towards the end. 
\end{abstract}

@@

\begin{figure}[!hb] 
% \renewcommand*{\thesubfigure}{}
\centering
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePSDPy.pdf}}
\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}
\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
\caption{Distribution of the parameters estimates over 272
runs.}
\label{fig:Parameters}
\end{figure}
\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.

@@

\begin{eqnarray}\label{eq:IntegralOfGaussian}

@@
